Plots_manuscript_v0.3

### 2020-07-31 R/Plots_manuscript_v0.3.Rmd
Start GWAS G BLUP eight site Results section

h2gr <- h2gr %>%
  full_join(h2gr_gxe)
h2fl <- h2fl %>%
  full_join(h2fl_gxe)
```
### older files to load
h2fl <- read_csv("~/Github/pvdiv-phenology-gxe/analysis/heritability/h2_df_FL50_related_functions_of_weather_v3.csv")
h2gr <- read_csv("~/Github/pvdiv-phenology-gxe/analysis/heritability/h2_df_GR50_related_functions_of_weather_v2.csv")
h2gr4 <- read_csv(file.path(workingdir, "analysis", "heritability", "h2_df_GR50_related_functions_of_weather_v4.csv"))
h2gr <- h2gr %>%
  full_join(h2gr4)

# Overview
Here I'm putting the code for any new analyses that I'm running to do new writeup for the manuscript v0.3.

@@

@@

for(i in seq_along(subpop_v)){
  for(j in seq_along(set_v)){
    dir.create(file.path(outputdir, names(set_v)[j]), showWarnings = FALSE)
    snp <- snp_attach(inputfiles$SNPfiles[i])
    phe_df <- read_csv(file.path(inputdir, paste0("BLUP_phenotypes_",
                                                  "for_gwas_GR_FL_",
                                                  names(subpop_v)[i],
                                                  ".csv"))) 
  if(names(set_v)[j] != "single_sites"){
    phe_df <- phe_df %>%
    select(PLANT_ID, ends_with(names(set_v)[j]))
  } else {
    phe_df <- phe_df %>%
    select(PLANT_ID, !ends_with("sites"))
  }
  pvdiv_standard_gwas(snp, df = phe_df, type = "linear", 
                      outputdir = file.path(outputdir, names(set_v)[j]),
                      savegwas = TRUE, saveannos = TRUE, txdb = txdb,
                      minphe = 130)

@@

```{r}
gwasdir <- file.path(workingdir, "analysis", "gwas", "G_BLUP")
log10p_gulf <- readRDS(file.path(gwasdir,                                 "log10p_strong_df_1000topSNPs_GR_FL_Gulf.rds"))
log10p_midw <- readRDS(file.path(gwasdir,                                 "log10p_strong_df_1000topSNPs_GR_FL_Midwest.rds"))
log10p_gandm <- readRDS(file.path(gwasdir,                                 "log10p_strong_df_1000topSNPs_GR_FL_Gulf_and_Midwest.rds"))
```

```{r}
log10p_gulf %>%
  pivot_longer(cols = -(SNP:POS), names_to = "PHE", values_to = "log10p") %>%
  ungroup() %>%
  filter(log10p > -log10(0.05/10300000)) %>%
  group_by(PHE) %>%
  tally() %>%
  write_csv(., "../manuscript/tables/Gulf_SNPs_above_Bonferroni_by_trait.csv")
```

```{r}
log10p_midw %>%
  pivot_longer(cols = -(SNP:POS), names_to = "PHE", values_to = "log10p") %>%
  ungroup() %>%
  filter(log10p > -log10(0.05/8800000)) %>%
  group_by(PHE) %>%
  tally() %>%
  write_csv(., "../manuscript/tables/Midwest_SNPs_above_Bonferroni_by_trait.csv")

log10p_gandm %>%
  pivot_longer(cols = -(SNP:POS), names_to = "PHE", values_to = "log10p") %>%
  ungroup() %>%
  filter(log10p > -log10(0.05/12100000)) %>%
  group_by(PHE) %>%
  tally() %>%
  write_csv(., "../manuscript/tables/Gulf_and_Midwest_diversity_panel_SNPs_above_Bonferroni_by_trait.csv")
```

```{r}
gulf_top <- readRDS(file.path(gwasdir, "Part-One-Output_Top-Effects-1000-SNPs_GR_FL_Gulf.rds"))

gulf_top %>%
  group_by(n_cond_in_top_set) %>%
  tally()

gulf_top_manh2 <- gulf_top %>%
  filter(max_score_log10p > 5.897) %>%
  ggplot(aes(x = POS, y = max_score_log10p)) + 
  geom_point(aes(color = Condition, shape = as_factor(n_cond_in_top_set))) + 
  #geom_line(aes(group = Condition)) +
  facet_wrap( ~ CHR, nrow = 1, scales = "free_x", strip.position = "bottom") +
  theme(legend.position = "top",
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        panel.background = element_rect(fill=NA)) +
        labs(x = "Chromosome", y = "-log10(p value)") +
        scale_x_continuous(expand = c(0.18, 0.18)) +
  scale_color_viridis(discrete = TRUE, end = 0.97) +
  scale_shape_manual(values = c(4, 16, 17, 18, 14, 3, 4))
save_plot("../manuscript/plots/Gulf_G_BLUP_top_500_Manhattan_2.png", base_height = 5, base_asp = 2.5, plot = gulf_top_manh2)

gulf_top_manh <- gulf_top %>%
  filter(max_score_log10p > 5.897) %>%
  ggplot(aes(x = POS, y = max_score_log10p)) + 
  geom_point(aes(color = n_cond_in_top_set, shape = Condition)) + 
  #geom_line(aes(group = Condition)) +
  facet_wrap( ~ CHR, nrow = 1, scales = "free_x", strip.position = "bottom") +
  theme(legend.position = "top",
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        panel.background = element_rect(fill=NA)) +
        labs(x = "Chromosome", y = "-log10(p value)") +
        scale_x_continuous(expand = c(0.18, 0.18)) +
  scale_color_viridis(option = "B", end = 0.9) +
  scale_shape_manual(values = c(15, 16, 17, 18, 14, 3, 4))

save_plot("../manuscript/plots/Gulf_G_BLUP_top_500_Manhattan.png", base_height = 5, base_asp = 2.5, plot = gulf_top_manh)
```

```{r}
midw_top <- readRDS(file.path(gwasdir, "Part-One-Output_Top-Effects-1000-SNPs_GR_FL_Midwest.rds"))

midw_top %>%
  group_by(n_cond_in_top_set) %>%
  tally()

midw_top_manh2 <- midw_top %>%
  filter(max_score_log10p > 6) %>%
  ggplot(aes(x = POS, y = max_score_log10p)) + 
  geom_point(aes(color = Condition, shape = as_factor(n_cond_in_top_set))) + 
  #geom_line(aes(group = Condition)) +
  facet_wrap( ~ CHR, nrow = 1, scales = "free_x", strip.position = "bottom") +
  theme(legend.position = "top",
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        panel.background = element_rect(fill=NA)) +
        labs(x = "Chromosome", y = "-log10(p value)") +
        scale_x_continuous(expand = c(0.18, 0.18)) +
  scale_color_viridis(discrete = TRUE, end = 0.97) +
  scale_shape_manual(values = c(4, 16, 17, 18, 14, 3, 4))
save_plot("../manuscript/plots/Midwest_G_BLUP_top_500_Manhattan_2.png", base_height = 5, base_asp = 2.5, plot = midw_top_manh2)

midw_top_manh <- midw_top %>%
  filter(max_score_log10p > 5.897) %>%
  ggplot(aes(x = POS, y = max_score_log10p)) + 
  geom_point(aes(color = n_cond_in_top_set, shape = Condition)) + 
  #geom_line(aes(group = Condition)) +
  facet_wrap( ~ CHR, nrow = 1, scales = "free_x", strip.position = "bottom") +
  theme(legend.position = "top",
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        panel.background = element_rect(fill=NA)) +
        labs(x = "Chromosome", y = "-log10(p value)") +
        scale_x_continuous(expand = c(0.18, 0.18)) +
  scale_color_viridis(option = "B", end = 0.9) +
  scale_shape_manual(values = c(15, 16, 17, 18, 14, 3, 4))

save_plot("../manuscript/plots/Midwest_G_BLUP_top_500_Manhattan.png", base_height = 5, base_asp = 2.5, plot = midw_top_manh)
```

```{r}
gandm_top <- readRDS(file.path(gwasdir, "Part-One-Output_Top-Effects-1000-SNPs_GR_FL_Gulf_and_Midwest.rds"))

gandm_top %>%
  group_by(n_cond_in_top_set) %>%
  tally()

gandm_top_manh2 <- gandm_top %>%
  filter(max_score_log10p > 6) %>%
  ggplot(aes(x = POS, y = max_score_log10p)) + 
  geom_point(aes(color = Condition, shape = as_factor(n_cond_in_top_set))) + 
  #geom_line(aes(group = Condition)) +
  facet_wrap( ~ CHR, nrow = 1, scales = "free_x", strip.position = "bottom") +
  theme(legend.position = "top",
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        panel.background = element_rect(fill=NA)) +
        labs(x = "Chromosome", y = "-log10(p value)") +
        scale_x_continuous(expand = c(0.18, 0.18)) +
  scale_color_viridis(discrete = TRUE, end = 0.97) +
  scale_shape_manual(values = c(4, 16, 17, 18, 14, 3, 4))
save_plot("../manuscript/plots/Gulf_and_Midwest_G_BLUP_top_500_Manhattan_2.png", base_height = 5, base_asp = 2.5, plot = gandm_top_manh2)

gandm_top_manh <- gandm_top %>%
  filter(max_score_log10p > 5.897) %>%
  ggplot(aes(x = POS, y = max_score_log10p)) + 
  geom_point(aes(color = n_cond_in_top_set, shape = Condition)) + 
  #geom_line(aes(group = Condition)) +
  facet_wrap( ~ CHR, nrow = 1, scales = "free_x", strip.position = "bottom") +
  theme(legend.position = "top",
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        panel.background = element_rect(fill=NA)) +
        labs(x = "Chromosome", y = "-log10(p value)") +
        scale_x_continuous(expand = c(0.18, 0.18)) +
  scale_color_viridis(option = "B", end = 0.9) +
  scale_shape_manual(values = c(15, 16, 17, 18, 14, 3, 4))

save_plot("../manuscript/plots/Gulf_and_Midwest_G_BLUP_top_500_Manhattan.png", base_height = 5, base_asp = 2.5, plot = gandm_top_manh)
```

## Overlap with QTL and between subpops
```{r}

>>>>

h2gr <- h2gr %>%
  full_join(h2gr_gxe)
h2fl <- h2fl %>%
  full_join(h2fl_gxe)
```a the code for any new analyses that I'm running to do new writeup for the manuscript v0.3.

@@

sites %>% arrange(manu_site)
```

@@

for(j in 4){#seq_along(set_v)){
  for(i in seq_along(subpop_v)){
    dir.create(file.path(outputdir, names(set_v)[j]), showWarnings = FALSE)
    snp <- snp_attach(inputfiles$SNPfiles[i])
    phe_df <- read_csv(file.path(inputdir, paste0("BLUP_phenotypes_",
                                                  "for_gwas_GR_FL_",
                                                  names(subpop_v)[i],
                                                  ".csv"))) 
  if(names(set_v)[j] != "single_sites"){
    phe_df <- phe_df %>%
    dplyr::select(PLANT_ID, ends_with(names(set_v)[j]))
  } else {
    phe_df <- phe_df %>%
    dplyr::select(PLANT_ID, !ends_with("sites"))
    if(names(subpop_v)[i] != "Gulf"){
      phe_df <- phe_df %>%
    dplyr::select(PLANT_ID, ends_with("NE"), ends_with("MI"), ends_with("SD"))
    }
  }
  pvdiv_standard_gwas(snp, df = phe_df, type = "linear", 
                      outputdir = file.path(outputdir, names(set_v)[j]),
                      savegwas = TRUE, saveannos = TRUE, txdb = txdb,
                      minphe = 130)

@@

gwasdir <- file.path(workingdir, "analysis", "gwas", "G_BLUP")
log10p_gulf <- readRDS(file.path(gwasdir,                                 "log10p_strong_df_1000topSNPs_GR_FL_Gulf.rds"))
log10p_midw <- readRDS(file.path(gwasdir,                                 "log10p_strong_df_1000topSNPs_GR_FL_Midwest.rds"))
log10p_gandm <- readRDS(file.path(gwasdir,                                 "log10p_strong_df_1000topSNPs_GR_FL_Gulf_and_Midwest.rds"))

```{r}
j=1
i=3

names(set_v)[j]
names(subpop_v)[i]
bonferroni_v <- c(-log10(0.05/12100000), -log10(0.05/8800000), -log10(0.05/10300000))

gwasdir <- file.path(workingdir, "analysis", "gwas", "BLUPs", names(set_v)[j])
log10p_gulf <- readRDS(file.path(gwasdir, 
                                 paste0("log10p_strong_df_1000topSNPs_",
                                        "FL_", names(set_v)[j], "_Gulf",
                                        ".rds")))
log10p_midw <- readRDS(file.path(gwasdir,
                                 paste0("log10p_strong_df_1000topSNPs_", "FL_",
                                 names(set_v)[j], "_", "Midwest.rds")))
log10p_gandm <- readRDS(file.path(gwasdir,
                                  paste0("log10p_strong_df_1000topSNPs_",
                                         "FL_", names(set_v)[j], "_",
                                         "Gulf_and_Midwest.rds")))
log10p_df <- readRDS(file.path(gwasdir,
                                  paste0("log10p_strong_df_1000topSNPs_",
                                         "FL_", names(set_v)[j], "_",
                                         names(subpop_v)[i], ".rds")))
```

```{r}
log10p_gulf %>%
  pivot_longer(cols = -(SNP:POS), names_to = "PHE", values_to = "log10p") %>%
  ungroup() %>%
  filter(log10p > -log10(0.05/10300000)) %>%
  group_by(PHE) %>%
  tally() #%>%
  #write_csv(., paste0("../manuscript/tables/Gulf_", names(set_v)[j], "_SNPs_above_Bonferroni_by_trait.csv"))

log10p_midw %>%
  pivot_longer(cols = -(SNP:POS), names_to = "PHE", values_to = "log10p") %>%
  ungroup() %>%
  filter(log10p > -log10(0.05/8800000)) %>%
  group_by(PHE) %>%
  tally() #%>%
  #write_csv(., paste0("../manuscript/tables/Midwest_", names(set_v)[j], "_SNPs_above_Bonferroni_by_trait.csv"))

log10p_gandm %>%
  pivot_longer(cols = -(SNP:POS), names_to = "PHE", values_to = "log10p") %>%
  ungroup() %>%
  filter(log10p > -log10(0.05/12100000)) %>%
  group_by(PHE) %>%
  tally() #%>%
  #write_csv(., paste0("../manuscript/tables/Gulf_and_Midwest_", names(set_v)[j], "__SNPs_above_Bonferroni_by_trait.csv"))
  #
log10p_gandm %>%
  pivot_longer(cols = -(SNP:POS), names_to = "PHE", values_to = "log10p") %>%
  ungroup() %>%
  filter(log10p > -log10(0.05/12100000)) %>%
  mutate(Pos_Mb = floor(POS/100000)/10) %>%
  group_by(CHR, Pos_Mb) %>% tally()
bonferroni <- -log10(0.05/12100000)
log10p_gandm %>%
  filter(cgdd_12c_gr2fl_eight_sites_log10p > -log10(0.05/12100000) |
         FL50_eight_sites_log10p > -log10(0.05/12100000)) %>%
  group_by(cgdd_12c_gr2fl_eight_sites_log10p > FL50_eight_sites_log10p) %>%
  tally()
log10p_gandm %>%
  filter(dyln_fl50_eight_sites_log10p > -log10(0.05/12100000)  |
         FL50_eight_sites_log10p > -log10(0.05/12100000)) %>%
  group_by(dyln_fl50_eight_sites_log10p > FL50_eight_sites_log10p) %>%
  tally()

log10p_gandm %>%
  ggplot(aes(x = dyln_fl50_eight_sites_log10p, y = FL50_eight_sites_log10p)) + 
  geom_point(alpha = 0.5) + 
  geom_abline(slope = 1, intercept = 0, linetype = 2) +
  geom_vline(xintercept = bonferroni, color = "red", linetype = 2) + 
  geom_hline(yintercept = bonferroni, color = "red", linetype = 2)
```
```{r}
i=1 # subpop
j=3 # site set

names(set_v)[j]
names(subpop_v)[i]
bonferroni_v <- c(-log10(0.05/12100000), -log10(0.05/8800000), -log10(0.05/10300000))

gwasdir <- file.path(workingdir, "analysis", "gwas", "BLUPs", names(set_v)[j])
log10p_df <- readRDS(file.path(gwasdir,
                                  paste0("log10p_strong_df_1000topSNPs_",
                                         "FL_", names(set_v)[j], "_",
                                         names(subpop_v)[i], ".rds")))
top_set <- readRDS(file.path(gwasdir, 
                                paste0("Part-One-Output_Top-Effects-1000-SNPs_",
                                        "FL_", names(set_v)[j], "_",
                                        names(subpop_v)[i], ".rds")))

log10p_df %>%
  pivot_longer(cols = -(SNP:POS), names_to = "PHE", values_to = "log10p") %>%
  ungroup() %>%
  filter(log10p > bonferroni_v[i]) %>%
  group_by(CHR, POS) %>% tally()
log10p_df %>%
  pivot_longer(cols = -(SNP:POS), names_to = "PHE", values_to = "log10p") %>%
  ungroup() %>%
  filter(log10p > bonferroni_v[i]) %>%
  mutate(Pos_Mb = floor(POS/100000)/10) %>%
  group_by(CHR, Pos_Mb) %>% tally()

top50 <- top_set %>% ungroup() %>%
  top_n(100, max_score_log10p) %>%
  mutate(SNP = paste(CHR, POS, sep = "_"))
dyln_binom <- log10p_df %>%
  filter(SNP %in% top50$SNP) %>%
  group_by(dyln_fl50_north_sites_log10p > FL50_north_sites_log10p) %>%
  tally()
binom.test(x = dyln_binom$n[2], n = 100, alternative = "greater")

cgdd_binom <- log10p_df %>%
  filter(SNP %in% top50$SNP) %>%
  group_by(cgdd_12c_gr2fl_north_sites_log10p > FL50_north_sites_log10p) %>%
  tally()
binom.test(x = cgdd_binom$n[2], n = 100, alternative = "greater")

log10p_df %>%
  ggplot(aes(x = dyln_fl50_north_sites_log10p, y = FL50_north_sites_log10p)) + 
  geom_point(alpha = 0.5) + 
  geom_abline(slope = 1, intercept = 0, linetype = 2) +
  geom_vline(xintercept = bonferroni_v[i], color = "red", linetype = 2) + 
  geom_hline(yintercept = bonferroni_v[i], color = "red", linetype = 2)
```

## Plot top GWAS hits
```{r}
for(i in seq_along(subpop_v)){
  for(j in 1:3){
    gwasdir <- file.path(workingdir, "analysis", "gwas", "BLUPs",
                         names(set_v)[j])
    top_set <- readRDS(file.path(gwasdir, 
                                paste0("Part-One-Output_Top-Effects-1000-SNPs_",
                                        "FL_", names(set_v)[j], "_",
                                        names(subpop_v)[i], ".rds")))
    top_set %>%
      group_by(n_cond_in_top_set) %>%
      tally()

    top_manh2 <- top_set %>%
      filter(max_score_log10p > 5.897) %>%
      ggplot(aes(x = POS, y = max_score_log10p)) + 
      geom_point(aes(color = Condition, shape = as_factor(n_cond_in_top_set))) + 
      #geom_line(aes(group = Condition)) +
      facet_wrap( ~ CHR, nrow = 1, scales = "free_x", 
                  strip.position = "bottom") +
      theme(legend.position = "top",
            axis.text.x = element_blank(), axis.ticks.x = element_blank(),
            panel.background = element_rect(fill=NA)) +
            labs(x = "Chromosome", y = "-log10(p value)") +
            scale_x_continuous(expand = c(0.18, 0.18)) +
      scale_color_viridis(discrete = TRUE, end = 0.97) +
      scale_shape_manual(values = c(4, 16, 17, 18, 14, 3, 4))
    save_plot(paste0("../manuscript/plots/", "FL_", names(set_v)[j], "_",
                     names(subpop_v)[i], "_top_500_Manhattan.png"), 
              base_height = 5, base_asp = 2.5, plot = top_manh2)

  }
}
```

## Overlap with QTL and between subpops

Comparing the top 100 hits within and between subpopulations, X of Y were found in the same 100kb regions.
```{r}
i=3 # subpop
j=1 # site set

names(set_v)[j]
names(subpop_v)[i]
bonferroni_v <- c(-log10(0.05/12100000), -log10(0.05/8800000), -log10(0.05/10300000))

top_pos <- list()

gwasdir <- file.path(workingdir, "analysis", "gwas", "BLUPs", names(set_v)[j])
log10p_df <- readRDS(file.path(gwasdir,
                                  paste0("log10p_strong_df_1000topSNPs_",
                                         "FL_", names(set_v)[j], "_",
                                         names(subpop_v)[i], ".rds")))
for(i in 1:3){
top_set <- readRDS(file.path(gwasdir, 
                                paste0("Part-One-Output_Top-Effects-1000-SNPs_",
                                        "FL_", names(set_v)[j], "_",
                                        names(subpop_v)[i], ".rds")))

top_pos[[i]] <- top_set %>%
  ungroup() %>%
  top_n(n = 100, wt = max_score_log10p) %>%
  mutate(Pos_Mb = floor(POS/100000)/10) %>%
  group_by(CHR, Pos_Mb) %>%
  tally()
}

gandm_m <- top_pos[[1]] %>%
  inner_join(top_pos[[2]])
gandm_g <- top_pos[[1]] %>%
  inner_join(top_pos[[3]])
m_g <- top_pos[[2]] %>%
  inner_join(top_pos[[3]])
c(nrow(gandm_m)/nrow(top_pos[[1]]), nrow(gandm_m)/nrow(top_pos[[2]]),
  nrow(gandm_g)/nrow(top_pos[[1]]), nrow(gandm_g)/nrow(top_pos[[3]]),
  nrow(m_g)/nrow(top_pos[[2]]), nrow(m_g)/nrow(top_pos[[3]])
  )

top50 <- top_set %>% ungroup() %>%
  top_n(100, max_score_log10p) %>%
  mutate(SNP = paste(CHR, POS, sep = "_"))
dyln_binom <- log10p_df %>%
  filter(SNP %in% top50$SNP) 
```

```{r}
i=3 # subpop
j=1 # site set

names(set_v)[j]
names(subpop_v)[i]
bonferroni_v <- c(-log10(0.05/12100000), -log10(0.05/8800000), -log10(0.05/10300000))

top_pos <- list()

log10p_df <- readRDS(file.path(gwasdir,
                                  paste0("log10p_strong_df_1000topSNPs_",
                                         "FL_", names(set_v)[j], "_",
                                         names(subpop_v)[i], ".rds")))
for(j in 1:3){
  gwasdir <- file.path(workingdir, "analysis", "gwas", "BLUPs", names(set_v)[j])
  top_set <- readRDS(file.path(gwasdir, 
                                paste0("Part-One-Output_Top-Effects-1000-SNPs_",
                                        "FL_", names(set_v)[j], "_",
                                        names(subpop_v)[i], ".rds")))

top_pos[[j]] <- top_set %>%
  ungroup() %>%
  top_n(n = 500, wt = max_score_log10p) %>%
  mutate(Pos_Mb = floor(POS/100000)/10) %>%
  group_by(CHR, Pos_Mb) %>%
  tally()
}

gandm_m <- top_pos[[1]] %>%
  inner_join(top_pos[[2]])
gandm_g <- top_pos[[1]] %>%
  inner_join(top_pos[[3]])
m_g <- top_pos[[2]] %>%
  inner_join(top_pos[[3]])
c(nrow(gandm_m)/nrow(top_pos[[1]]), nrow(gandm_m)/nrow(top_pos[[2]]),
  nrow(gandm_g)/nrow(top_pos[[1]]), nrow(gandm_g)/nrow(top_pos[[3]]),
  nrow(m_g)/nrow(top_pos[[2]]), nrow(m_g)/nrow(top_pos[[3]])
  )

top50 <- top_set %>% ungroup() %>%
  top_n(100, max_score_log10p) %>%
  mutate(SNP = paste(CHR, POS, sep = "_"))
dyln_binom <- log10p_df %>%
  filter(SNP %in% top50$SNP) 
```
for gulf and midwest:
4.3-6.5% overlap in top 100 between eight and tx; no overlap in top 100 between eight and north or north and texas.
500: 8% eight and texas; 1.6% eight and north. 0.9% north and texas.

for midwest:
5% overlap in top 500 eight and texas; 18% overlap eight and north; 1.7% north and texas.

for gulf:
6.2% overlap eight and texas in top 500; 5.2% overlap eight and north; 2.7% overlap north and texas.

I think the top 500 SNPs are good here - give you large enough numbers.
